Multimodal spatial availability: a singly-constrained measure of accessibility considering multiple modes

### 2023-12-02 Journal-manuscript/Journal-manuscript.Rmd
Small tweaks to R1 manuscript as requested by the journal office

```{r, jobs-plot, fig.cap="\\label{fig:Fig2} Distribution of jobs taken by people living and working in Madrid as reported in the 2018 travel survey. Grey TAZs has no jobs. Ranges of values in the legend are quintiles.", fig.show='hold', fig.align='center'}
knitr::include_graphics("images/Fig2.png") 
```

```{r, pop-plot, fig.cap="\\label{fig:Fig3} Population living and working in Madrid by mode of transportation as reported in the 2018 travel survey. Grey TAZs have no population. Ranges of values in the legend are quintiles.", fig.show='hold', fig.align='center'}
knitr::include_graphics("images/Fig3.png")
```

@@

In this example, we use all home-to-full-time-work trips, by all modes. The trips are expanded using population weights. Figures \ref{fig:Fig2} and \ref{fig:Fig3} show the number of workers and the distribution of full-time jobs in the City of Madrid by TAZ. The light grey boundary represents the LEZ Centro in effect in 2017. The survey was conducted after the introduction of LEZ Centro. The dark grey boundary represents the LEZ planned for the boundaries of the M-30 highway and is present in the plots as a spatial reference for areas in proximity to the LEZ Centro.

@@

```{r, SA-m-plot, fig.cap="\\label{fig:Fig5} Spatial availability of jobs per origin and mode $V_i^m$ in Madrid. Grey TAZs have no population. Ranges of values in the legend are quintiles.", fig.show='hold', fig.align='center', fig.height=10}
knitr::include_graphics("images/Fig5.png")
```

@@

```{r, SA-per-capita-m-plot, fig.cap="\\label{fig:Fig7} Distribution of spatially available jobs per capita by mode of transportatin ($v_i^m$). Grey TAZs have no population that use the mode. Ranges of values in the legend are quintiles.", fig.show='hold', fig.align='center', fig.height=10}
knitr::include_graphics("images/Fig7.png")
```

@@

# Acknowledgements

This research was funded by the Canada Graduate Scholarship - Doctoral Program (CGS D) provided by the Social Sciences and Humanities Research Council (SSHRC) and Project Mobilizing Justice, also supported by SSHRC. The funders had no role in study design, data collection and analysis, decision to publish, or preparation of the manuscript.

All work is fully-reproducible and available within this [GitHub repository](https://github.com/soukhova/Multimodal-spatial-availability).

>>>>

```{r, jobs-plot, fig.cap="\\label{fig:Fig2} Distribution of jobs taken by people living and working in Madrid as reported in the 2018 travel survey. Grey TAZs have no jobs. Ranges of values in the legend are quintiles. The TAZ shapefile is available from the Community of Madrid open data portal.", fig.show='hold', fig.align='center'}
knitr::include_graphics("images/Fig2.png") 
```

```{r, pop-plot, fig.cap="\\label{fig:Fig3} Population living and working in Madrid by mode of transportation as reported in the 2018 travel survey and represented at the level of TAZ. Grey TAZ have no population. Ranges of values in the legend are quintiles. The TAZ shapefile is available from the Community of Madrid open data portal.", fig.show='hold', fig.align='center'}
knitr::include_graphics("images/Fig3.png")
```

@@

In this example, we use all home-to-full-time-work trips, by all modes. The trips are expanded using population weights. Figures \ref{fig:Fig2} and \ref{fig:Fig3} show the number of workers and the distribution of full-time jobs in the City of Madrid by TAZ. The TAZ shapefiles are available from the Community of Madrid open data portal [@comunidaddemadridzoniEDM20182020]. The light grey boundary represents the LEZ Centro in effect in 2017. The survey was conducted after the introduction of LEZ Centro. The dark grey boundary represents the LEZ planned for the boundaries of the M-30 highway and is present in the plots as a spatial reference for areas in proximity to the LEZ Centro.

@@

```{r, SA-m-plot, fig.cap="\\label{fig:Fig5} Spatial availability of jobs per origin and mode $V_i^m$ in Madrid at the level of TAZ. Grey TAZ have no population. Ranges of values in the legend are quintiles. The TAZ shapefile is available from the Community of Madrid open data portal.", fig.show='hold', fig.align='center', fig.height=10}
knitr::include_graphics("images/Fig5.png")
```

@@

```{r, SA-per-capita-m-plot, fig.cap="\\label{fig:Fig7} Distribution of spatially available jobs per capita by mode of transportatin ($v_i^m$) represented at the level of TAZ. Grey TAZ have no population that use the mode. Ranges of values in the legend are quintiles. The TAZ shapefile is available from the Community of Madrid open data portal.", fig.show='hold', fig.align='center', fig.height=10}
knitr::include_graphics("images/Fig7.png")
```

@@

<!-- # Acknowledgements -->

<!-- This research was funded by the Canada Graduate Scholarship - Doctoral Program (CGS D) provided by the Social Sciences and Humanities Research Council (SSHRC) and Project Mobilizing Justice, also supported by SSHRC. The funders had no role in study design, data collection and analysis, decision to publish, or preparation of the manuscript. -->

<!-- All work is fully-reproducible and available within this [GitHub repository](https://github.com/soukhova/Multimodal-spatial-availability). -->
